---
title: "Task 7"
author: "Sabrina Olmo"
date: "9/15/2022"
output: 
  html_document:
    keep_md:  TRUE 
    code_folding: 'hide'
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidyverse)
library(knitr)
download.file("https://raw.githubusercontent.com/hadley/r4ds/master/data/heights.csv", "Height")
HeightData <- read_csv("Height")
str(HeightData)
```

```{r}
HeightEd <- HeightData %>%
              mutate(ed = fct_collapse(as.factor(ed),
                            primary = c("3","4","5","6"),
                            secondary = c("7","8","9","10","11"),
                            highschoolgrad = ("12"),
                            associate = c("13","14","15"),
                            bachelors = ("16"),
                            mastersdoctorate = c("17","18"))) 
```

```{r}
ggplot(HeightEd) +
  geom_bar(aes(x = ed, fill = race), position = "dodge") +
  labs(title = "Race by Education Level",
       x = "Education Level",
       y = "Count")

ggplot(HeightEd) +
  geom_bar(aes(x = ed, fill = sex), position = "dodge") +
  labs(title = "Sex by Education Level",
       x = "Education Level",
       y = "Count")

Earning_Edu <- filter(HeightEd, ed %in% c("highschoolgrad", "associate", "bachelors", "mastersdoctorate")) 

arrow_data1 <- data.frame(x1 = "associate", y1 = 175000, x2 = "bachelors", y2 = 175000)

ggplot(Earning_Edu) +
  geom_boxplot(aes(x = ed, y = earn, fill = sex)) +
  geom_segment(aes(x = x1, y = y1, xend = x2, yend = y2), color = "blue", data = arrow_data1,
               arrow = arrow(length = unit(0.1, "in"))) +
  labs(title = "Earnings by Education Level Split Between Men and Women ",
       x = "Education Level",
       y = "Earnings") +
  annotate("text", x = "associate", y = 150000, label = "Highest paid Bachelors level man makes 
           more than highest paid Masters level woman", size = 3.5)
```

Looking at the data, we can see that women do not get paid as much as men even though they have the same education levels. In some cases, a man with a lower education level than a woman could get paid more even though she went further in school. Using a boxplot allowed me to see the gender discrepencies a bit better because it includes the average range of pay for each gender. A few of the male boxes have a wider range which shows that men have a wider pay range than women in some cases.