---
title: "Task 14"
author: "Sabrina Olmo"
date: "10/11/2022"
output:
  html_document:
    keep_md: yes
    code_folding: hide
  pdf_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, message = FALSE}
library(tidyverse)
library(stringi)
library(knitr)
```

```{r Data, message = FALSE}
dat <- tempfile()
download.file("https://github.com/WJC-Data-Science/DTS350/raw/master/bible.csv", "dat")
bible <- read_csv("dat")
```

```{r Q1}
Old_Testament <- bible %>%
        filter(volume_title == "Old Testament") %>%
          select(scripture_text)

New_Testament <- bible %>%
        filter(volume_title == "New Testament") %>%
          select(scripture_text)

length_function <- function(df) {
  verse_length <- vector("integer", 0)
  for (row in df) {verse_length <- append(verse_length, str_length(row))}
  verse_length
}
  
mean(length_function(Old_Testament))
mean(length_function(New_Testament))
```

```{r Q2}
str_length(str_extract_all(Old_Testament, "(?i)lord"))
str_length(str_extract_all(New_Testament, "(?i)lord"))
```

```{r Q3}
NT_word_count <- bible %>%
  filter(volume_title == "New Testament") %>%
  select(book_title, verse_id, scripture_text) %>%
  group_by(book_title) %>%
  mutate(word_count = str_count(scripture_text, '\\W+'))
  
ggplot(NT_word_count, aes(x = book_title, y = mean(word_count))) +
  geom_col(aes(fill = book_title)) +
  coord_flip() +
  labs(title = "Word Count by Verse, New Testament",
       x = "Book Title",
       y = "Word Count") +
  theme(legend.position = "none")
```
When we split up the bible by the 2 main sections, we can see that the Old Testament has on average more words than the New Testament. The word "lord" no matter how it is written appears more in the Old Testament by a considerable margin. Finally we can see that in the New Testament Matthew, Luke, John, and Acts have on average more words than all of the other books in the New Testament. 
