---
title: "Case Study 12"
author: "Sabrina Olmo"
date: "11/17/2022"
output:
  html_document:
    keep_md: yes
    code_folding: hide
  pdf_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, message = FALSE}
library(tidyverse)
library(tidyquant)
library(lubridate)
library(gganimate)
library(gifski)
library(dygraphs)
library(timetk)
```

```{r Getting Data}
avocado <- read_csv("avocado.csv")

state_data <- avocado %>%
                filter(region == "California")

US_data <- avocado %>%
              filter(region == "TotalUS") %>%
              rename("TotalVolume" = "Total Volume")

region_data <- avocado %>%
                filter(region %in% c("GreatLakes", "Midsouth", "Northeast", "NorthernNewEngland",
                                   "Plains", "SouthCentral", "Southeast", "West", "WestTexNewMexico")) %>%       
                rename("TotalVolume" = "Total Volume") %>%
                mutate(year = year(Date))

city_data <- avocado %>%
              filter(!region %in% c("GreatLakes", "Midsouth", "Northeast", "NorthernNewEngland",
                                   "Plains", "SouthCentral", "Southeast", "West", "WestTexNewMexico", 
                                   "California", "TotalUS")) %>%
              rename("TotalVolume" = "Total Volume")

costalcities <- city_data %>%
                  filter(region %in% c("LosAngeles", "SanDiego", "SanFrancisco",
                                       "MiamiFtLauderdale", "Tampa", "Portland"))
```

```{r AvocadoPlots}
USplot <- ggplot(US_data) +
          geom_line(aes(x = Date, y = AveragePrice)) +
          labs(title = "Date: {frame_along}",
               x = "Date",
               y = "Average Price") +
               theme_bw()

USplot + transition_reveal(Date)

Regionplot <- ggplot(data = region_data, mapping = aes(x = Date, y = AveragePrice, color = TotalVolume)) +
                geom_point(size = 0.25) +
                facet_wrap(~region) +
                shadow_trail(distance = 0.05) +
                labs(title = "Date: {frame_along}",
                             x = "Date",
                             y = "Average Price",
                     color = "Total Volume/1000") +
                             theme_bw()

Regionplot + transition_reveal(Date)

ggplot(costalcities) +
  geom_point(aes(x = Date, y = AveragePrice, color = region, size = TotalVolume/1000)) +
  facet_wrap(~region) +
  labs(title = "Avocado Prices by City",
       x = "Date",
       y = "AveragePrice") +
  theme_bw()
```
I chose to to use the cities that are on the coast for the last plot. To me it makes sense that the coastal cities would sell avocados for a somewhat lower price with the best quality because of the increasing availability compared to inland cities. Through this I would advise my friend to look for jobs in Los Angeles or Portland because it seems like the avocados are sold at a higher volume for a lower average price. We can see that the average prices for avocados are highest in San Francisco and Tampa, so I would not advise my friend to look for a job in those cities unless absolutely necessary. 

```{r StockData}
stocks <- tq_get(c("CVGW", "AVO"), get = "stock.prices", from = today() - years(2), to = today())

stockplot <- stocks %>%  
          select(symbol, date, adjusted) %>%
          pivot_wider(names_from = symbol, values_from = adjusted) %>%
          tk_xts(date_var = date) 

dygraph(stockplot, main = "Adjusted Values for AVO and CVGW Stocks") %>%
  dyAxis("y", label = "Adjusted")
```
Looking at the stock data we can see that CVGW has suffered a decrease in adjusted value but it is still higher than AVO which is much more consistent, but is also a lower value. Overall it seems like investing in avocado stocks are not the best investment. 