---
title: "Task 5"
author: "Sabrina Olmo"
date: "9/8/2022"
output: 
  html_document:
    keep_md:  TRUE 
    code_folding: 'hide'
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidyverse)
library(downloader)
library(knitr)
```

```{r}
SoloData <- read_csv("solo-artist-followers.csv")
BillboardData <- read_csv("billboard-hits.csv")
```

For the SoloData, all of the data types are chrs, for the BillboardData there are 3 chr types one date type and a dbl. All of the data imported correctly.

```{r}
head(BillboardData)
head(SoloData)
times_top_100 <- BillboardData %>%
                    filter(is.na(band) == FALSE) %>%                 
                    group_by(name, band) %>%
                    summarise(appearance = n()) %>%
                    filter(appearance > 6, na.rm = TRUE)

Solo_artist <- BillboardData %>%
  filter(name %in% times_top_100$name)
  
Bands <- BillboardData %>%
  filter(is.na(band) == TRUE) %>%
  filter(name %in% times_top_100$band)%>%
  mutate(band = name)

head(Bands)
head(times_top_100)

ggplot() +
  geom_point(Solo_artist, mapping = aes(x = peak_date, y = peak_rank, 
                                          color = name, group = name)) +
  geom_line(Solo_artist, mapping = aes(x = peak_date, y = peak_rank, 
                                          color = name, group = name)) +
  geom_point(Bands, mapping = aes(x = peak_date, y = peak_rank), color = "black") +
  geom_line(Bands, mapping = aes(x = peak_date, y = peak_rank), 
                                 color = "black", linetype = "dotted") +
  facet_wrap(~band, scales = "free")
```

```{r Data Set 1}
read_csv("covid-hospital.csv")
```

https://github.com/owid/covid-19-data/tree/master/public/data/hospitalizations
This source contains COVID hospital data from March 2020 to September 2022. The data shows the number of people hospitalized in different countries on given days.
```{r Data Set 2}
read_csv("covid-daily-tests.csv")
```

https://ourworldindata.org/coronavirus-testing#testing-for-covid-19-background-the-our-world-in-data-covid-19-testing-dataset
This source gives covid testing information from Janurary 2020 to June 2022. The number of tests by thousand is recored on a 7 day period. 

```{r Data Set 3}
library(readxl)
read_xlsx("covid19-table1.xlsx")
```

https://www.bls.gov/cps/effects-of-the-coronavirus-covid-19-pandemic.htm
This data set contains information about employees who have worked at home due to covid in the last month by demographic.