---
title: "Case Study 4"
author: "Sabrina Olmo"
date: "9/16/2022"
output: 
  html_document:
    keep_md:  TRUE 
    code_folding: 'hide'
editor_options: 
  chunk_output_type: console
---

```{r Installing packages}
library(tidyverse)
library(knitr)
library(nycflights13)
```

Which origin airport is best to minimize my chances of a late arrival when I am using Delta Airlines?
```{r Question 2}
flights %>%
  count(as.factor(carrier))

Airlineflights <- flights %>%
                  mutate(carrier = fct_recode(carrier,
                               Endeavor = "9E",
                               American = "AA",
                               Alaska = "AS",
                               JetBlue = "B6",
                               Delta = "DL",
                               ExpressJet = "EV",
                               Frontier = "F9",
                               AirTran = "FL",
                               Hawaiian = "HA",
                               Envoy = "MQ",
                               SkyWest = "OO",
                               United = "UA",
                               USAir = "US",
                               Virgin_America = "VX",
                               Southwest = "WN",
                               Mesa = "YV"))
         
delaydat <- Airlineflights %>%
              select(origin, carrier, arr_delay) %>%
                filter(carrier == "Delta") %>%
                  group_by(origin) %>%
                    summarise(Avgdelay = mean(arr_delay, na.rm = TRUE))

ggplot(delaydat, mapping = aes(x = reorder(origin, Avgdelay), y = Avgdelay, fill = origin)) +
  geom_col(position = position_dodge(0.25), width = 0.5) +
  geom_text(aes(label =round(Avgdelay, digits = 2)), hjust = "inward", vjust = "inward") +
  coord_flip() +
  labs(title = "Average Delay Time by Origin Airport",
       x = "Average Delay Time", 
       y = "Origin Airport")
```
We can see that JFK is the only origin airport with a negative mean arrival delay time. On average, in 2013 flights arrived around 2 minutes early into JFK, compared to almost 4 minutes late into LGA and almost 9 minutes late into EWR.


Which destination airport is the worst airport for arrival time?
```{r Question 3}
flights %>%
  count(as.factor(dest))

worst_dest <- flights %>%
                group_by(dest) %>%
                  summarise(dest_delay = mean(arr_delay, na.rm = TRUE)) %>%
                    filter(dest_delay >= 15)

ggplot(worst_dest) +
  geom_col(aes(x = reorder(dest, dest_delay), y = dest_delay, fill = dest), 
           position = "dodge") +
  labs(title = "Destination Airports with Greater Than 15 Min Arrival Delays",
       x = "Destination Airport", 
       y = "Average Arrival Delay Time") +
  theme_light()
```
We can see that the CAE destination airport has the highest average arrival delay by a considerable amount. I wanted to filter the dataset to only include the destination airports with arrival times of greater than 15 minutes. 
